\documentclass[11pt]{article}

\usepackage{natbib}
\usepackage{setspace}
\usepackage[left=2.5cm,top=2.8cm,right=2.5cm,bottom=2.8cm]{geometry}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{theorem}
\usepackage{version}
\usepackage{multirow}
\usepackage{amssymb}
\usepackage{tikz}
\usetikzlibrary{arrows,arrows.meta,decorations,decorations.pathreplacing,calc,matrix}

\definecolor{Red}{rgb}{1,0,0}
\definecolor{Blue}{rgb}{0,0,1}
\definecolor{Green}{rgb}{0,1,0}
\definecolor{magenta}{rgb}{1,0,.6}
\definecolor{lightblue}{rgb}{0,.5,1}
\definecolor{lightpurple}{rgb}{.6,.4,1}
\definecolor{gold}{rgb}{.6,.5,0}
\definecolor{orange}{rgb}{1,0.4,0}
\definecolor{hotpink}{rgb}{1,0,0.5}
\definecolor{newcolor2}{rgb}{.5,.3,.5}
\definecolor{newcolor}{rgb}{0,.3,1}
\definecolor{newcolor3}{rgb}{1,0,.35}
\definecolor{darkgreen1}{rgb}{0, .35, 0}
\definecolor{darkgreen}{rgb}{0, .6, 0}
\definecolor{darkred}{rgb}{.75,0,0}
\definecolor{lightgrey}{rgb}{.7,.7,.7}

\definecolor{clemson-orange}{RGB}{234,106,32}
\definecolor{chicago-maroon}{RGB}{128,0,0}
\definecolor{northwestern-purple}{RGB}{82,0,99}
\definecolor{cornell-red}{RGB}{179,27,27}
\definecolor{sauder-green}{RGB}{171,180,0}
\definecolor{lawngreen}{RGB}{0,250,154}

\setcounter{MaxMatrixCols}{10}

\onehalfspacing
\newtheorem{theorem}{Theorem}
\newtheorem{acknowledgement}{Acknowledgement}
\newtheorem{algorithm}{Algorithm}
\newtheorem{assumption}{Assumption}
\newtheorem{axiom}{Axiom}
\newtheorem{case}{Case}
\newtheorem{claim}{Claim}
\newtheorem{conclusion}{Conclusion}
\newtheorem{condition}{Condition}
\newtheorem{conjecture}{Conjecture}
\newtheorem{corollary}{Corollary}
\newtheorem{criterion}{Criterion}
\newtheorem{definition}{Definition}
\newtheorem{example}{Example}
\newtheorem{exercise}{Exercise}
\newtheorem{lemma}{Lemma}
\newtheorem{notation}{Notation}
\newtheorem{problem}{Problem}
\newtheorem{proposition}{Proposition}
{\theorembodyfont{\normalfont}
\newtheorem{remark}{Remark}
}
\newtheorem{summary}{Summary}
\newenvironment{proof}[1][Proof]{\textbf{#1.} }{\hfill \rule{0.5em}{0.5em} \bigskip}
\newenvironment{soln}[1][Soln]{\textbf{#1:} }{\hfill \rule{0.5em}{0.5em}}
\renewcommand{\cite}{\citeasnoun}
\renewcommand{\theenumii}{(\alph{enumii})}
\renewcommand{\labelenumii}{\theenumii}
\renewcommand{\theenumiii}{\roman{enumiii}}
\renewcommand{\labelenumiii}{\theenumiii.}

\usepackage[nameinlink]{cleveref}
\crefname{assumption}{Assumption}{Assumptions}
\crefname{lemma}{Lemma}{Lemmas}
\crefname{theorem}{Theorem}{Theorems}
\crefname{corollary}{Corollary}{Corollaries}
\crefname{proposition}{Proposition}{Propositions}
\crefname{claim}{Claim}{Claims}
\crefname{procedure}{Procedure}{Procedures}
\crefname{algorithm}{Algorithm}{Algorithms}
\crefname{figure}{Figure}{Figures}
\crefname{remark}{Remark}{Remarks}
\crefname{section}{Section}{Sections}
\crefname{procedure}{Procedure}{Procedures}
\crefname{example}{Example}{Examples}
\crefname{definition}{Definition}{Definitions}
\crefname{table}{Table}{Tables}
\crefname{align}{}{}
\crefname{enumi}{}{}
\crefname{conjecture}{Conjecture}{Conjectures}
\crefname{step}{Step}{Steps}
\crefname{appendix}{Appendix}{Appendices}
\crefname{footnote}{Footnote}{Footnotes}

\begin{document}


\begin{center}
\textbf{ECON 201 Week 6 Problem Set}\\
\textit {Professor: Teddy kim};  
Sunday, October 16th.
\\Student name: Hridansh Saraogi
\end{center}

\begin{enumerate}
\item For each of the following statements, determine whether
the statement is \emph{true} or \emph{false} (the latter including ``not necessarily true''), and provide a brief explanation.

    \begin{enumerate}
   	\item A risk-loving decision-maker always takes a risky bet.
        \begin{enumerate}
            \item False\\
            A risk-loving decision-maker will take a risky bet, as long as it is fair.
            \item For eg: Risk lovers take the risks when two lotteries are of the same expected value. \\
            Since the expected value of one lottery may be higher or lower, they will be willing to take risks only if the lottery is fair.
        \end{enumerate}
	
	\item If two lotteries have the same expected value but different variances, then a risk-averse person always prefers the lottery with a higher variance.
	    \begin{enumerate}
	        \item False\\
	        A risk averse person would only prefer the lottery with a lower variance when the expected values are the same. \\In this case, only risk lovers would want to choose the lottery with the higher variance.
	    \end{enumerate}

    \item If a risk-averse person is willing to take a risky investment, then a risk-neutral person with the same income is willing to take the same risky investment.
        \begin{enumerate}
            \item True\\
            A risk averse person does not like to take risks and has a tendency to avoid them. \\In contrast, a risk neutral person is rather insensitive to risk and by nature, is willing to take more risks than a risk averse person
            \item In this scenario, if a risk averse person (someone who does not like taking risks) is willing to take a risky investment, then a risk-neutral person (who takes more risks than a risk averse person) \textbf{will be willing to take the same risky investment}
            \item In other words (and focusing on expected value): If a risk averse person takes the risk, it must be that the expected value of the risky investment is much higher than the one without the risk. And we know that risk neutral people only care about expected values. Since the expected value of the investment is much higher, risk neutral person would also prefer the risk.
        \end{enumerate}

    \item Lane is not risk averse. If he is offered a chance to pay \$10 for a lottery ticket that will give him a prize of \$100 with probability .06, a prize of \$50 with probability .1, and no prize with probability .84, then he will buy the ticket.
        \begin{enumerate}
            \item True\\
            \item The Expected Value of Lane choosing the lottery is: \\
            $100 (0.06) + 50(0.1) + 0.84(0)$\\
            = 11 - cost of ticket = 11 - 10\\
            = 1 
            \item The Expected Value of Lane not choosing the lottery is 1(0) = 0 \\
            Since $1 > 0$, and Lane is not risk averse, she would buy the loterry ticket
        \end{enumerate}

    \end{enumerate}

\item Qing just inherited a vineyard from a distant relative. In good years, she earns \$216 from the sale of grapes from the vineyard. If the weather is poor, she earns only \$27. Qing's estimate of the probability of good weather is $2/3$.
	\begin{enumerate}
	\item Compute the expected value and the variance of Qing's income from the vineyard.
	    \begin{enumerate}
	        \item Expected Value: \\
	        $\frac{2}{3}*216 + \frac{1}{3}*27 = 153$
	        \item Variance:\\
	        $\frac{1}{3}*(27-153)^2 + \frac{2}{3}*(216-153)^2$\\
	        = 7938
	    \end{enumerate}
	
	\item Qing is risk averse. William, a grape buyer, offers Qing a guaranteed payment of \$153 each year in exchange for her entire harvest. Will Qing accept the offer? Provide a brief explanation.
	    \begin{enumerate}
	        \item Yes, Qing will accept the offer because both the outcomes (running the vineyard herself, and giving the entire harvest to William) give the same Expected Value
	        \item This scenario is similar to having two lotteries with the same expected value. In such a case Qing would prefer the one with lower risk because she is risk averse.
	        \item Thus, in the vineyard case, Qing would accept William’s offer as she is then able to shift the risk from herself, to William.
	        
	    \end{enumerate}
	
	\item Suppose that Qing's utility function is given by $u(v)=v^{1/3}$. Find the lowest guaranteed payment Qing would accept (in other words, the price at which Qing is indifferent between accepting and rejecting William's offer).
	    \begin{enumerate}
	        \item U(L): $\frac{2}{3}(216)^\frac{1}{3}$ + $\frac{1}{3}(27)^\frac{1}{3}$ = 5 \\
	        5 = CE$^\frac{1}{3}$\\
	        $5^3 = CE^\frac{1}{3}^3$
	        \item 125 = CE\\
	        Hence, the lowest guaranteed payment Qing would accept is 125. This is the price at which Qing is indifferent between accepting and rejecting William's offer.
	    \end{enumerate}
    \end{enumerate}

\item If you remain healthy, you expect to earn an income of \$160,000. If, by contrast, you become disabled, you will only be able to work part time, and your average income will drop to \$40,000. Suppose that you believe that there is a 5 percent chance that you could become disabled. Furthermore, your utility function is $\sqrt{I}$.
    \begin{enumerate}
    \item What is your expected income? What is your expected utility?
        \begin{enumerate}
            \item Expected Income:\\
            EV(I) = $\frac{95}{100}(160,000) + \frac{5}{100}(40,000) $\\
            = \$154,000
            \item Expected Utility:\\
            U(I) = $\frac{95}{100}\sqrt{160,000} + \frac{5}{100}\sqrt{40,000}$\\
            = 390
        \end{enumerate}

    \item Consider an insurance policy that fully insures you in the event that you are disabled. What is the actuarially fair insurance premium? In other words, suppose that you pay $x$ for an insurance that gives you \$120,000 extra income when you become disabled. For what value of $x$ is the insurance actuarially fair?
        \begin{enumerate}
            \item Actuarially Fair is the scenario when the insurance company will be indifferent to offering you the policy - they will not gain or lose in strictly monetary terms
            \item Let us begin by calculating the coverage required for every \$1 premium:\\
            $\frac{1}{p}=\frac{1}{0.05}=20$
            \item 160,000 - X = 40,000 - X + 20X\\
            120,000 = 20X\\
            X = 6,000
            \item The insurance would be actuarially fair when the value of $x$ is \$6,000
        \end{enumerate}

    \item What is the highest premium that you would be willing to pay for the full insurance policy?
        \begin{enumerate}
            \item $\sqrt{(160,000-x)} = 390$\\
            x = 7900
            \item Therefore, the highest premium that I would be willing to pay for the full insurance policy is \$7,900
        \end{enumerate}
    \end{enumerate}
        
\end{enumerate}

\end{document}


