\documentclass[11pt]{article}

\usepackage{natbib}
\usepackage{setspace}
\usepackage[left=2.5cm,top=2.8cm,right=2.5cm,bottom=2.8cm]{geometry}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{theorem}
\usepackage{version}
\usepackage{multirow}
\usepackage{amssymb}
\usepackage{tikz}
\usetikzlibrary{arrows,arrows.meta,decorations,decorations.pathreplacing,calc,matrix}

\definecolor{Red}{rgb}{1,0,0}
\definecolor{Blue}{rgb}{0,0,1}
\definecolor{Green}{rgb}{0,1,0}
\definecolor{magenta}{rgb}{1,0,.6}
\definecolor{lightblue}{rgb}{0,.5,1}
\definecolor{lightpurple}{rgb}{.6,.4,1}
\definecolor{gold}{rgb}{.6,.5,0}
\definecolor{orange}{rgb}{1,0.4,0}
\definecolor{hotpink}{rgb}{1,0,0.5}
\definecolor{newcolor2}{rgb}{.5,.3,.5}
\definecolor{newcolor}{rgb}{0,.3,1}
\definecolor{newcolor3}{rgb}{1,0,.35}
\definecolor{darkgreen1}{rgb}{0, .35, 0}
\definecolor{darkgreen}{rgb}{0, .6, 0}
\definecolor{darkred}{rgb}{.75,0,0}
\definecolor{lightgrey}{rgb}{.7,.7,.7}

\definecolor{clemson-orange}{RGB}{234,106,32}
\definecolor{chicago-maroon}{RGB}{128,0,0}
\definecolor{northwestern-purple}{RGB}{82,0,99}
\definecolor{cornell-red}{RGB}{179,27,27}
\definecolor{sauder-green}{RGB}{171,180,0}
%\definecolor{gray}{RGB}{192,192,192}
\definecolor{lawngreen}{RGB}{0,250,154}

\setcounter{MaxMatrixCols}{10}

\onehalfspacing
\newtheorem{theorem}{Theorem}
\newtheorem{acknowledgement}{Acknowledgement}
\newtheorem{algorithm}{Algorithm}
\newtheorem{assumption}{Assumption}
\newtheorem{axiom}{Axiom}
\newtheorem{case}{Case}
\newtheorem{claim}{Claim}
\newtheorem{conclusion}{Conclusion}
\newtheorem{condition}{Condition}
\newtheorem{conjecture}{Conjecture}
\newtheorem{corollary}{Corollary}
\newtheorem{criterion}{Criterion}
\newtheorem{definition}{Definition}
\newtheorem{example}{Example}
\newtheorem{exercise}{Exercise}
\newtheorem{lemma}{Lemma}
\newtheorem{notation}{Notation}
\newtheorem{problem}{Problem}
\newtheorem{proposition}{Proposition}
{\theorembodyfont{\normalfont}
\newtheorem{remark}{Remark}
}
\newtheorem{summary}{Summary}
\newenvironment{proof}[1][Proof]{\textbf{#1.} }{\hfill \rule{0.5em}{0.5em} \bigskip}
\newenvironment{soln}[1][Soln]{\textbf{#1:} }{\hfill \rule{0.5em}{0.5em}}
\renewcommand{\cite}{\citeasnoun}
\renewcommand{\theenumii}{(\alph{enumii})}
\renewcommand{\labelenumii}{\theenumii}
\renewcommand{\theenumiii}{\roman{enumiii}}
\renewcommand{\labelenumiii}{\theenumiii.}

\usepackage[nameinlink]{cleveref}
\crefname{assumption}{Assumption}{Assumptions}
\crefname{lemma}{Lemma}{Lemmas}
\crefname{theorem}{Theorem}{Theorems}
\crefname{corollary}{Corollary}{Corollaries}
\crefname{proposition}{Proposition}{Propositions}
\crefname{claim}{Claim}{Claims}
\crefname{procedure}{Procedure}{Procedures}
\crefname{algorithm}{Algorithm}{Algorithms}
\crefname{figure}{Figure}{Figures}
\crefname{remark}{Remark}{Remarks}
\crefname{section}{Section}{Sections}
\crefname{procedure}{Procedure}{Procedures}
\crefname{example}{Example}{Examples}
\crefname{definition}{Definition}{Definitions}
\crefname{table}{Table}{Tables}
\crefname{align}{}{}
\crefname{enumi}{}{}
\crefname{conjecture}{Conjecture}{Conjectures}
\crefname{step}{Step}{Steps}
\crefname{appendix}{Appendix}{Appendices}
\crefname{footnote}{Footnote}{Footnotes}

\begin{document}


\begin{center}
\textbf{ECON 201 Week 4 Problem Set}\\
\textit {Professor: Teddy kim};  
Sunday, September 25th.
\\Group 3: Hridansh Saraogi, Lia Sidberry, Sherlyn Shao
\end{center}

\begin{enumerate}
\item For each of the following statements, determine whether
the statement is \emph{true} or \emph{false} (the latter including ``not necessarily true''), and provide a brief explanation.

    \begin{enumerate}
    \item If you always spends 10\% of your income to buy apples, then apples are a luxury good to you.
    \begin{enumerate}
        \item False. It is homothetic\\
        The definition of luxury goods is that a consumer consumes proportionally more as her income rises. \item Thus, the consumption proportion of apples should not be fixed. It should be determined by the percentage change in income.
    \end{enumerate}

    \item It is impossible for all goods to be inferior goods.
    \begin{enumerate}
        \item True\\
        When total income increases, consumption decreases.
        \item If all goods are inferior then we are not maximizing our utility because we won’t spend all of our income.
    \end{enumerate}

    \item If a good is an inferior good, then an increase in its price will increase the demand for it.
    \begin{enumerate}
        \item False\\
        If a good is a giffen good, then an increase in price increases the demand for it.
        \item However, we know that giffen good is just a type of inferior good and not all goods are Giffen good.
    \end{enumerate}

    \item An increase in the price of a Giffen good makes the people who consume that good better off.
    \begin{enumerate}
        \item Not necessarily true (False)\\
        Because the increase in price will cause an increase in demand. But this increase in demand will cause the consumer to have to pay more money for the Giffen good. Since they will have to pay more, it does not necessarily mean that they will be better off.
    \end{enumerate}

    \item If leisure is a normal good, then an increase in non-labor income will reduce labor supply.
    \begin{enumerate}
        \item True. If leisure is a normal good, and there is an increase in non-labor income, people will:\\ Reduce their working hours and this will reduce the supply of labor, causing the labor supply curve to shift to the left.
        \item Further Explanation: Increasing non-labor income will lead to an increase in leisure which will cause a decrease in actual labor. This signifies a decrease in the labor supply.
    \end{enumerate}

\end{enumerate}

\pagebreak
\item Suppose Bella's preferences for apples $(x_{1})$ and bananas $(x_{2})$ can be represented by the following utility function: $u(x_{1},x_{2})=x_{1}x_{2}^{2}$.
    \begin{enumerate}
        \item Derive Bella's demand function (as a function of $p_{1}$, $p_{2}$, and $m$).
        \begin{enumerate}
            \item Demand function:
            \item Suppose $u(x_1, x_2) = x_1(x_2)^2$
            \item Given $(p_1, p_2, m)$, the consumer's problem is:\\
            $max_{(x_1, x_2)} x_1(x_2)^2$ subject to $p_1x_1 + p_2x_2 \leq m$
            \item Arbitrage Method:\\
            Budget constraint: $p_1x_1 + p_2x_2 \leq m$\\
            Slope Condition: $MRS_{12} = \frac{MU_1}{MU_2} = \frac{x^2_2}{2x_1x_2} = \frac{x_2}{2x_1} = \frac{p_1}{p_2} \hspace{1cm} \rightarrow \hspace{1cm} 2p_1x_1 = p_2x_2$
            \item Solving the above system of equations:\\
            $x_1(p_1, p_2, m)=x_1^* = \frac{m}{3p_1}, x_2(p_1, p_2, m) = x_2^* = \frac{2m}{3p_2}$
            \item Both are increasing in m, decreasing in own price, and independent of the other price.
        \end{enumerate}

        \item Compute Bella's income elasticity $\eta_{1}$ and price elasticity $\epsilon_{1}$ for apples.
        \begin{enumerate}
            \item Income elasticity: \\
            Cobb-Douglas: $u(x_{1},x_{2}) = x_1(x_2)^2$
            \item $x_1 = \frac{m}{3p_1} \hspace{1cm} \rightarrow \hspace{1cm} n_1 = \frac{\partial x_1}{\partial m} \frac{m}{x_1} = \frac{1}{3p_1} \frac{m}{\frac{m}{3p_1}} = 1$\\
            Good $x_1$ is a homothetic good
            \item Price Elasticity:\\
            $\frac{\partial x_1}{\partial_p1} \frac{p_1}{x_1} = \frac{-m}{3p_1^2} \frac{p_1}{\frac{m}{3p_1}} = -1$
            \item $\frac{-m}{3p_1^2}*\frac{3p_1^2}{m}$ = -1\\
            Therefore, we can conclude that it is unit elastic.
        \end{enumerate}

        \item Suppose $p_{2}=2$ and $m=18$. If the price of apples decreases from $p_{1}=2$ to $p_{1}^{\prime}=1$, then how does Bella's demand for apples change?
        \begin{enumerate}
            \item Old budget line, before price change:\\
            $2x_1 + 2x_2 = 18$
            \item $MRS_1_2 = \frac{x_2}{2x_1}=\frac{2}{2}=2x_1 = x_2$
            \item $3x_2 = 18$\\
            $x_2 = 6$; $x_1 = 3$
            \item New Budget line, after price change:\\
            $x_1 + 2x_2 = 18$
            \item $MRS_1_2 = \frac{x_2}{2x_1}=\frac{p_1^'}{p_2}=\frac{1}{2}$
            \item $2x_2 = 2x_1$\\$x_2 = x_1$\\
            $3x_1 = 18$
            \item $x_1 = 6$; $x_2 = 6$
            \item Demand for $x_1$ increased from 3 to 6; demand increased by 3 apples
        \end{enumerate}

        \item Compute how much is due to the substitution effect in (c).
        \begin{enumerate}
            \item Before the price change, $p_1 = 2$; $p_2 = 2$\\
            Optimal Consumption Bundle: (3, 6)\\
            Utility of consumption is: $3*6^2 = 108$
            \item $MRS_1_2 = \frac{x_2}{2x_1} = \frac{p_1^'}{p_2} = \frac{1}{2}$
            \item $2x_1 = 2x_1$\\
            $x_1^3 = 108$\\
            $x_1 = 108^{\frac{1}{3}}$
            \item The substitution effect is equal to $108^{\frac{1}{3}} - 3$
        \end{enumerate}

    \end{enumerate}


\item Ruohong likes to add 2 teaspoons of sugar $(x_{2})$ to each cup of coffee $(x_{1})$. Formally, her preferences for coffee and sugar can be represented by $u(x_{1},x_{2})=\min\{2x_{1},x_{2}\}$.

    \begin{enumerate}
        \item Derive Ruohong's demand function for coffee (as a function of $p_{1}$, $p_{2}$, and $m$).
        \begin{enumerate}
            \item $u(x_1, x_2) = min{\{2x_1, x_2\}}$
            \item This is an example of Perfect Complements
            \item It is optimal when $2x_1 = x_2$
            \item Budget Line: $p_1x_1 + p_2x_2 = m$\\
            $p_1x_1 + p_22x_1 = m$
            \item Demand function: $x_1 = \frac{m}{p_1+2p_2}$\\
            $x_2 = \frac{2m}{p_1+2P_2}$
        \end{enumerate}

        \item Compute Ruohong's income elasticity $\eta_{1}$ and price elasticity $\epsilon_{1}$ for apples. Is coffee a luxury, a necessity, or a homothetic good to Ruohong? Is Ruohong's demand for coffee elastic, inelastic, or unit-elastic?
        \begin{enumerate}
            \item Income Elasticity $n_1 = \frac{\partial x_1}{\partial m}*\frac{m}{x_1}$
            \item $\frac{1}{p_1 + 2p_2}*\frac{m}{\frac{m}{p_1+2p_2}} = 1 = homothetic$
            \item Price Elasticity $E_1 = \frac{\partial x_1}{\partial p_1}*\frac{p_1}{x_1}=\frac{-m}{(p_1+2p_2)^2}*\frac{p_1}{1}*\frac{(p_1+2p_2)^2}{m}$
            \item $\frac{-p_1}{p_1+2p_2} > -1$\\
            Hence we conclude it is Inelastic
        \end{enumerate}

        \item Suppose $p_{2}=2$ and $m=30$. If the price of coffee increases from $p_{1}=1$ to $p_{1}^{\prime}=2$, then how does Ruohong's demand for coffee?
        \begin{enumerate}
            \item Demand decreases from 6 to 5; demand decreased by 1 unit
        \end{enumerate}

        \item Compute how much is due to the substitution effect in (c).
        \begin{enumerate}
            \item The substitution effect is 0 because point B exists at the same tangent of the old indifference curve and the slope of the new budget line.
            They are perfect complements of each other
        \end{enumerate}

    \end{enumerate}



\end{enumerate}

\end{document}


